\documentclass[11pt]{article}

% =========================
% Basic packages
% =========================
\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{array}
\usepackage{parskip}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

% =========================
% Spacing controls
% =========================
\newcommand{\PARSKIP}{0.5em}
\newcommand{\SECTOP}{1.6em}
\newcommand{\SECBOT}{1.0em}
\newcommand{\ITEMTOP}{0.5em}
\newcommand{\ITEMSEP}{0.45em}
\newcommand{\HEADBOT}{1.5em}

\setlength{\parskip}{\PARSKIP}
\setlength{\parindent}{0pt}

% =========================
% Section style
% =========================
\titleformat{\section}{\large\scshape\raggedright}{}{0pt}{}[\titlerule]
\titlespacing*{\section}{0pt}{\SECTOP}{\SECBOT}

% =========================
% List spacing
% =========================
\setlist[itemize]{leftmargin=1.5em,topsep=\ITEMTOP,itemsep=\ITEMSEP,parsep=0.2em}
\setlist[enumerate]{leftmargin=1.5em,topsep=\ITEMTOP,itemsep=\ITEMSEP,parsep=0.2em}

% =========================
% Commands
% =========================
\newcommand{\entry}[2]{\noindent\textbf{#1}\hfill #2\\}
\newcommand{\subentry}[2]{\noindent #1\hfill \emph{#2}\\}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcommand{\dateditem}[2]{\item \textbf{#1} \hfill #2}
\newcommand{\course}[1]{\textit{#1}}

% Entry with Expected line
\newcommand{\entryexp}[3]{%
	\noindent
	\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}} l r}
		\textbf{#1} & #2 \\
		& \emph{#3} \\
	\end{tabular*}\par
}

\begin{document}
	
	% =========================
	% Header
	% =========================
	\begin{center}
		{\Huge \textbf{Yuge Wang}}\\[0.9em]
		Email: \href{mailto:yuge.wang@uga.edu}{yuge.wang@uga.edu} \quad | \quad
		Website: \href{https://www.yugewang.com}{www.yugewang.com}\\[0.6em]
		Ph.D. Candidate, Department of International Affairs\\
		School of Public and International Affairs, University of Georgia
		
		\vspace{1em}
		\emph{CV last updated: October 2025}
	\end{center}
	
	\vspace{\HEADBOT}
	
	% ============================================================
	\section*{Education}
	
	\entryexp
	{Ph.D. in Political Science and International Affairs, University of Georgia}
	{2022 -- 2026}
	{(Expected)}
	
	Major: Comparative Politics \quad|\quad Minor: Political Methodology\\[0.3em]
	\emph{Dissertation:} \textit{Competition and Cooperation: Elite Politics under Personalist Rule}\\[0.3em]
	\emph{Committee:} Rongbin Han (chair), Alexa Bankert, Joseph T.\ Ornstein, Shane P.\ Singh
	
	\entry{M.B.A. in Finance and Economics (with honors), University of Science and Technology of China}{2014}
	
	\entry{B.A. in Economics, Hangzhou Normal University}{2009}
	
	% ============================================================
	\section*{Academic Positions}
	\entry{Assistant Professor, School of Tourism Management and Service, Tourism College of Zhejiang}{2015 -- 2022}
	
	% ============================================================
	\section*{Research Interests}
	Authoritarian politics (regime personalization, elite behavior, political institutions, state--society relations, central--local interactions, propaganda, gender in politics); computational social science; China
	
	% ============================================================
	\section*{Peer-Reviewed Articles}
	\begin{itemize}
		\item \textbf{Yuge Wang} and Rongbin Han. “Authoritarian Elasticity: How Autocracies May Effectively Mobilize for Crisis Management.” \emph{Governance}, 2025, e70074. https://doi.org/10.1111/gove.70074.\\
		Presented at the ISA Annual Meeting, 2024.
	\end{itemize}
	
	
	\section*{Papers Under Review}
	\begin{itemize}
		\item \textbf{Yuge Wang}. ``Shadow Factions: The Dictator's Local Dilemma.'' \\
		\item \textbf{Yuge Wang}. ``Downward Pressure: How Elite Competition Mitigates Agency Problems under Personalist Rule.''\\
		Presented at the ISA Annual Meeting, 2025.
	\end{itemize}
	
	% ============================================================
	\section*{Working Papers}
	\begin{itemize}
		\item \textbf{Yuge Wang}. ``Adapting to Personalism: How Local Elites Respond to Power Personalization in China.''\\
		\item \textbf{Yuge Wang}. ``Centralizing the Narrative: How Protégés Construct Regime Personalization.''\\
		Presented at the APSA Annual Meeting, 2024; Atlanta Symposium on Political Science, 2025.
		\item \textbf{Yuge Wang}. ``By the Women, for the Regime: Female Cadres and Authoritarian Stability in China.''
		\item \textbf{Yuge Wang}. ``The Infallible Party: Why Autocracies Delete Their Own News.''
		\item Wendy Weile Zhou, Rongbin Han, and \textbf{Yuge Wang}. ``U.S. vs. China? Chinese Overseas Youths' Positioning amid Geopolitical Tensions.''
	\end{itemize}
	
	% ============================================================
	\section*{Other Conference Papers}
	\begin{itemize}
		\item \textbf{Yuge Wang} and Rongbin Han. ``Innovating Authoritarian Grassroots Control: The Grid Management System in China.''\\
		Presented at the APSA Annual Meeting, 2023.
	\end{itemize}
	
	% ============================================================
	\section*{Other Publications}
	\begin{itemize}
		\item \textbf{Yuge Wang} and Lei Ren. 2020. ``The Impact of Trade Conflicts on American Tourists to China: Demonstration and Prediction.'' \emph{Lüyou Luntan (Tourism Forum)} 13(4): 62--72. (In Chinese)
		\item \textbf{Yuge Wang} and Yongqi Wang. 2017. ``A Study on the Influencing Factors of American Tourists' Demand for China: Demonstration Based on a Bayesian Regularized BP Neural Network.'' \emph{Journal of Zhejiang Normal University (Natural Science Edition)} 40(4): 459--464. (In Chinese)
	\end{itemize}
	
	% ============================================================
	\section*{Teaching Experience}
	\textbf{University of Georgia}
	\begin{itemize}
		\item Instructor of Record: INTL 4361 -- Chinese Politics, \emph{Spring 2026 (scheduled)}
		\item Instructor of Record: INTL 4361 -- Chinese Politics, \emph{Fall 2025}
		\item Instructor of Record: INTL 4004E -- Data Analytics for International Policy, \emph{Summer 2025}
		\item Teaching Assistant: INTL 3200 -- Introduction to International Relations, \emph{Spring 2025} (with Dr.\ Saglam and Dr.\ Berejikian)
		\item Teaching Assistant: POLS 1101 -- American Government, \emph{Spring 2024; Fall 2023} (with Dr.\ Jeffrey Glas)
		\item Teaching Assistant: INTL 3300 -- Introduction to Comparative Politics, \emph{Spring 2023} (with Dr.\ Erin Little)
	\end{itemize}
	
	\textbf{Tourism College of Zhejiang}
	\begin{itemize}
		\item Instructor of Record: Principles of Economics \emph{(Fall semesters, 2015 -- 2022)}
		\item Instructor of Record: Financial Analysis \emph{(Spring semesters, 2015 -- 2022)}
		\item Instructor of Record: Online Marketing \emph{(Fall and Spring semesters, 2016 -- 2022)}
	\end{itemize}
	
	% ============================================================
	\section*{Datasets}
	\begin{itemize}
		\item Official WeChat news articles from China, 2013--present: 61 central-level accounts; newspapers, government release accounts, Cyberspace Administration offices, and Political and Legal Affairs Commissions across 31 provinces; official-release accounts and newspapers from all 333 prefectural-level cities. Includes newly published and deleted articles; updated annually.
		\item Biographical and tenure data on Chinese provincial and municipal Party secretaries, 2002--present.
	\end{itemize}
	
	% ============================================================
	\section*{Grants \& Awards}
	\begin{itemize}
		\item Graduate Research Grant, \$4{,}000 (2025), Department of International Affairs, UGA
		\item Travel Grant (2023--2025), Department of International Affairs, UGA
		\item Graduate Research Grant, \$2{,}000 (2023), Department of International Affairs, UGA
	\end{itemize}
	
	% ============================================================
	\section*{Work Experience}
	\begin{itemize}
		\item Methods Help Desk Support, School of Public and International Affairs, University of Georgia \hfill \emph{Fall 2025 -- Spring 2026}
		\item Research Assistant, Department of International Affairs, University of Georgia\\
		\quad With Dr.\ Rongbin Han \hfill \emph{Fall 2024; Spring 2023; Fall 2022}\\
		\quad With Dr.\ Amanda Murdie \hfill \emph{Fall 2022}
		\item Product Manager, China Construction Bank, Zhejiang Branch \hfill \emph{2014 -- 2015}
		\item Customer Manager, China Construction Bank, Hangzhou Xihu Branch \hfill \emph{2009 -- 2014}
	\end{itemize}
	
	% ============================================================
	\section*{Professional Skills}
	SPSS, Stata, MATLAB, R, Python, \LaTeX
	
	% ============================================================
	\section*{Additional Training}
	ICPSR, 2023 (in person)
	
	% ============================================================
	\section*{Languages}
	Chinese (native); English (fluent)
	
\end{document}
